Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-01-17 docs/msr.tex
added table with descriptive statistics
fix: median is now the median not the index
simplified table data
small steps in writing.

\author{
\IEEEauthorblockN{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: \{dimitro, bkarak, gousiosg, louridas, dds\}@aueb.gr}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology \\
Email: G.Gousios@tudelft.nl}
}

@@

\begin{IEEEkeywords}
Software Vulnerabilities, Static Analysis, Software Evolution, Maven, FindBugs.
\end{IEEEkeywords}

@@

A security-related bug is a programming error that introduces a potentially
exploitable weakness into a computer system. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. One of the most common
approaches to identify software vulnerabilities is {\it static analysis}. This
kind of analysis is performed by automated tools either on the program's source
or object code and without actually executing it.

@@

A snapshot of the maven repository - January 2012.

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: \{dimitro, bkarak, louridas, dds\}@aueb.gr}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology \\
Email: G.Gousios@tudelft.nl}
}

@@

\begin{IEEEkeywords}
Software Vulnerabilities, Static Analysis, Software Evolution, Software
Security, Maven, FindBugs.
\end{IEEEkeywords}

@@

A security-related bug is a programming error that introduces a potentially
exploitable weakness into a computer system. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs, little attention has been paid to
study them in relation to software evolution.

One of the most common approaches to identify software vulnerabilities is {\it static analysis}.
This kind of analysis is performed by automated tools either on the program's source
or object code and without actually executing it.

@@

The subject of our study was a snapshot of the maven repository. Before
analyzing the data of the repository we performed a number of functional fits
on the data.

First, we obtained the repository snapshot (January 2012) that was previously
used by -- et. al~\cite{}.

\begin{table}
\centering
\caption{Descriptive Statistics Measurements for the Maven Repository}
\label{tbl:repository}
\begin{tabular}{l r}
 \hline
Projects & 17,505\\
Versions (total) & 114,399\\
Min & 1\\
Max & 337\\
Mean & 6.54\\
Median & 3\\
Range & 336\\
1$^{st}$ Quartile & 1\\
3$^{rd}$ Quartile & 8\\
\hline
\end{tabular}
\end{table}
